Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-09 mu/article/article.tex
sab

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
found.
% 
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
local maxima are held for same polarization angles but for an energy range of
the incoming beam between 1.90\,eV and 2.05\,eV.
% 
In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
which the response is maximized for the \emph{up} structure. In the same figures
and frames we present in dashed lines, related to the right scale, the
corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
frames of those figures the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
Also we present two circled and square boxes indicating the value where the
angles of the spin velocity is parallel and perpendicular and the the
corresponding arrows is directed to the value of the response corresponding to
those angles.

>>>>

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
found.
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
local maxima are held for same polarization angles but for an energy range of
the incoming beam between 1.90\,eV and 2.05\,eV.
In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
which the response is maximized for the \emph{up} structure. In the same figures
and frames we present in dashed lines, related to the right scale, the
corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
frames of those figures the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
Also we present two circled and square boxes indicating the value where the
angles of the spin velocity is parallel and perpendicular and the the
corresponding arrows is directed to the value of the response corresponding to
those angles.
From Fig. \ref{fig:up-vaz-rag-1} we have that the maximum response is obtained
for an incoming beam with energy of 0.088\,eV and polarization angle
$\alpha=40^{\circ}$ resulting in a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=37.4$\,Km/s coming from the
contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
and $\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s and being this response the
absolute maximum of the spin velocity polarized in the $\mathrm{z}$ direction
for the \emph{up} structure and corresponding a velocity angle
$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
In the same figure the green circled box indicates the value for which the
polarization angle $\alpha$ and the response direction angle
$\gamma_{\mathrm{x}}(\omega)$ are collinear at $65.5^{\circ}$ and being almost
constant in the complete range corresponding to a response
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s indicated with the
green arrow; also the blue square box indicates the value for which the
polarization angle and the response angle are perpendicular corresponding to
$\alpha=155.5^{\circ}$ and corresponding to a response
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.5$\,Km/s indicated with the blue
arrow.
Now from Fig. \ref{fig:up-vaz-rag-2} we have that a local maxima of the response
is obtained for an incoming beam with energy of 0.912\,eV and same polarization
angle $\alpha=40^{\circ}$ resulting in a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s and corresponding a
velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the $xy$ plane. Again
the green circled box indicates the value for which the polarization angle
$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega)$ are
collinear corresponding to $78^{\circ}$ and having variations of $\pm 2^{\circ}$
for $0^{\circ} \leq \alpha \leq 122^{\circ}$; this value corresponds to a response $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=23.5$\,Km/s indicated with the green arrow. The blue square box indicates the value for which the polarization angle and the response angle are perpendicular corresponding to 
% WRONG
% $\alpha=78.5^{\circ}$ and being held for  and corresponding to a response $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=10.3$\,Km/s indicated with the blue arrow.
